### 2019-03-01 docs/notebooks/results.Rmd
update results notebooks with VGG16 figs

```{python}
TEST_RESULTS_DIR = '../../data/experiment_1/results'
epochs_list = [10, 50, 200, 400, 800]
ftr_results_list = []
sptl_results_list = []
for epochs in epochs_list:
    ftr_results = os.path.join(TEST_RESULTS_DIR, f'feature_search_alexnet_models/test_alexnet_trained_{epochs}_epochs.gz')
    ftr_results_list.append(ftr_results)
    sptl_results = os.path.join(TEST_RESULTS_DIR, f'spatial_config_search_alexnet_models/test_alexnet_trained_{epochs}_epochs.gz')
    sptl_results_list.append(sptl_results)
    ftr_v_spt_conj(ftr_results,
                   sptl_results,
                   epochs=epochs)
```

@@

```{python}
mn_slope_by_epoch(ftr_results_list, sptl_results_list, epochs_list)
```

>>>>

```{python}
TEST_RESULTS_DIR = '../../data/experiment_1/results'
epochs_list = [10, 50, 200, 400, 800]
ftr_results_list = []
sptl_results_list = []
for epochs in epochs_list:
    ftr_results = os.path.join(TEST_RESULTS_DIR, f'feature_search_alexnet_models/test_alexnet_trained_{epochs}_epochs.gz')
    ftr_results_list.append(ftr_results)
    sptl_results = os.path.join(TEST_RESULTS_DIR, f'spatial_config_search_alexnet_models/test_alexnet_trained_{epochs}_epochs.gz')
    sptl_results_list.append(sptl_results)
    ftr_v_spt_conj(ftr_results,
                   sptl_results,
                   epochs=epochs)
alexnet_results = {
    'ftr': ftr_results_list,
    'sptl': sptl_results_list,
}
```

@@

```{python}
mn_slope_by_epoch(alexnet_results['ftr'], alexnet_results['sptl'], epochs_list)
```

### Other CNN architectures also show similar effects
To test whether these effects resulted from the architecture of AlexNet or were more general, we repeated the simulations using the VGG16 architecture.

```{python}
TEST_RESULTS_DIR = '../../data/experiment_1/results'
epochs_list = [10, 50, 200, 400, 800]
ftr_results_list = []
sptl_results_list = []
for epochs in epochs_list:
    ftr_results = os.path.join(TEST_RESULTS_DIR, f'feature_search_vgg16_models/test_VGG16_trained_{epochs}_epochs.gz')
    ftr_results_list.append(ftr_results)
    sptl_results = os.path.join(TEST_RESULTS_DIR, f'spatial_config_search_vgg16_models/test_VGG16_trained_{epochs}_epochs.gz')
    sptl_results_list.append(sptl_results)
vgg16_results = {
    'ftr': ftr_results_list,
    'sptl': sptl_results_list,
}

ftr_v_spt_conj(vgg16_results['ftr'][3],
               vgg16_results['sptl'][3],
               epochs=epochs_list[3])
```

We again saw this effect became stronger the more that the VGG16 architecture was trained.

```{python}
mn_slope_by_epoch(vgg16_results['ftr'], vgg16_results['sptl'], epochs_list)
```
